\bf Model Visualization Techniques for a Social Network Model

### 2017-07-05 PaperToDo.Rmd
baby steps

- [ ] Add histogram of number of tie changes from $t_1$ to $t_2$ in simulations 
- [ ] Make gif available online
- [ ] Insert link to full gif in paper
- [ ] Figure 6: reverse order of adjacency matrix y-axis
- [ ] Figure 7 not showing up??
- [ ] Fix error on p. 21 (probably related to above)
- [ ] Heatmap p 23 missing caption
- [ ] Describe Figure 8 more. What is going on??
- [ ] Add geomnet example in 4.2
- [ ] p. 26-28 figure refs & code is broken
- [ ] Get rid of repeated plot p 29
- [ ] p. 34 code is broken
- [ ] General proof reading

>>>>

- [ ] Add histogram of number of tie changes from $t_1$ to $t_2$ in simulations 
- [ ] Make gif available online
- [ ] Insert link to full gif in paper
- [X] Figure 6: reverse order of adjacency matrix y-axis
- [ ] Figure 7 not showing up??
- [ ] Fix error on p. 21 (probably related to above)
- [ ] Heatmap p 23 missing caption
- [ ] Describe Figure 8 more. What is going on??
- [ ] Add geomnet example in 4.2
- [ ] p. 26-28 figure refs & code is broken
- [ ] Get rid of repeated plot p 29
- [ ] p. 34 code is broken
- [ ] General proof reading

### 2017-07-05 paper.Rnw
baby steps

numordersf$from <- factor(numordersf$from, levels = paste0("V", 1:16))
numordersf$to <- factor(numordersf$to, levels = paste0("V", 1:16))

p1 <- ggplot(data = numordersf, aes(x = from, y = to)) + geom_tile(color = 'black', aes(fill = as.factor(value))) + 
  scale_fill_manual(values = c('white', 'black')) +
  theme(legend.position = 'none', axis.text = element_text(size = 8)) + 
  coord_fixed()

@@

pcaordersf$from <- factor(pcaordersf$from, levels = order1)
pcaordersf$to <- factor(pcaordersf$to, levels = order1)

p2 <- ggplot(data = pcaordersf, aes(x = from, y = to)) + geom_tile(color = 'black', aes(fill = as.factor(value))) + 
  scale_fill_manual(values = c('white', 'black')) +
  theme(legend.position = 'none', axis.text = element_text(size = 8)) + 
  coord_fixed()

>>>>

numordersf$from <- factor(numordersf$from, levels = paste0("V", 1:16))
numordersf$to <- factor(numordersf$to, levels = rev(paste0("V", 1:16)))

p1 <- ggplot(data = numordersf, aes(x = from, y = to)) + geom_tile(color = 'black', aes(fill = as.factor(value))) + 
  scale_fill_manual(values = c('white', 'black')) +
  theme(legend.position = 'none', axis.text = element_text(size = 8)) + 
  scale_x_discrete(position = "top") + 
  coord_fixed()

@@

pcaordersf$from <- factor(pcaordersf$from, levels = order1)
pcaordersf$to <- factor(pcaordersf$to, levels = rev(order1))

p2 <- ggplot(data = pcaordersf, aes(x = from, y = to)) + geom_tile(color = 'black', aes(fill = as.factor(value))) + 
  scale_fill_manual(values = c('white', 'black')) +
  theme(legend.position = 'none', axis.text = element_text(size = 8)) + 
  scale_x_discrete(position = "top") + 
  coord_fixed()
